Review of Assigned Readings

### 2018-01-02 paper/paper.tex
added package (subcaption) for horizontal alignment of images
reworked the graphs/tables and lists of graphs/tables

%************************** Useful packages **************************
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{csquotes}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[noconfigs,british]{babel}

@@

%************************** List of Figures ************************** 	
\listoffigures\bigskip\bigskip

@@

@@

	\begin{figure}[H]
	\graphicspath{ {stata_export_graphs/} }
	\includegraphics[scale=0.45]{graph_plot_nr_tweets.png}
	\end{figure}

	\begin{figure}[H]
	\graphicspath{ {stata_export_graphs/} }
	\includegraphics[scale=0.45]{graph_plot_df_nr_tweets.png}
	\end{figure}

	\begin{figure}[H]
	\graphicspath{ {stata_export_graphs/} }
	\includegraphics[scale=0.45]{graph_plot_log_df_nr_tweets.png}
	\end{figure}

	\begin{figure}[H]
	\graphicspath{ {stata_export_graphs/} }
	\includegraphics[scale=0.45]{graph_plot_bpi.png}
	\end{figure}

	\begin{figure}[H]
	\graphicspath{ {stata_export_graphs/} }
	\includegraphics[scale=0.45]{graph_plot_df_bpi.png}
	\end{figure}

	\begin{figure}[H]
	\graphicspath{ {stata_export_graphs/} }
	\includegraphics[scale=0.45]{graph_plot_log_df_bpi.png}
	\end{figure}

@@

\begin{figure}[H]
\centering
\graphicspath{ {stata_export_graphs/} }
\includegraphics[scale=0.85]{ADF_twitter_variables.png}
\end{figure}

@@

\begin{figure}[H]
\centering
\graphicspath{ {stata_export_graphs/} }
\includegraphics[scale=0.85]{ADF_bpi_variables.png}
\end{figure}

@@

\begin{figure}[H]
\centering
\graphicspath{ {stata_export_graphs/} }
\includegraphics[scale=0.85]{LAG_crit_df_nr_tweets_df_bpi.png}
\end{figure}

@@

\begin{tabular}{lcc} \hline
 & (T\textsubscript{t}) & (B\textsubscript{t}) \\
VARIABLES & df\_nr\_of\_tweets & df\_bpi\_closing\_price \\ \hline
 &  &  \\
L.df\_nr\_of\_tweets (T\textsubscript{t-1}) & 0.00999 (a\textsubscript{11}) & 0.00463 (a\textsubscript{21}) \\
 & (0.0693) & (0.0104) \\
L.df\_bpi\_closing\_price (B\textsubscript{t-1}) & -0.675 (a\textsubscript{12}) & -0.125* (a\textsubscript{22}) \\
 & (0.469) & (0.0707) \\
Constant  & -88.34 (c\textsubscript{1}) & -18.48 (c\textsubscript{2}) \\
 & (177.9) & (26.79) \\
 &  &  \\
 Observations & 205 & 205 \\ \hline
\multicolumn{3}{c}{ Standard errors in parentheses} \\
\multicolumn{3}{c}{ *** p$<$0.01, ** p$<$0.05, * p$<$0.1} \\
\end{tabular}

@@

\begin{figure}[H]
\centering
\graphicspath{ {stata_export_graphs/} }
\includegraphics[scale=0.85]{granger_test.png}
\end{figure}

>>>>

%************************** Useful packages **************************
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{csquotes}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[noconfigs,british]{babel}

@@

%************************** List of Figures ************************** 	
\listoffigures\bigskip\bigskip
\listoftables

@@

\begin{figure}[H]
	\begin{subfigure}{.3\textwidth}
	\centering
	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_nr_tweets.png}
	\caption{Number of Tweets regarding bitcoin}
	\end{subfigure}\hfill
	\begin{subfigure}{.3\textwidth}
	\centering
	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_df_nr_tweets.png}
	\caption{First difference of number of Tweets}
	\end{subfigure}\hfill
	\begin{subfigure}{.3\textwidth}
	\centering
	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_log_df_nr_tweets.png}
	\caption{Log first difference of number of Tweets}
	\end{subfigure}
\caption{Twitter variables development}
\end{figure}

@@

\begin{figure}[H]
	\begin{subfigure}{.3\textwidth}
	\centering
	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_bpi.png}
	\caption{Hourly development of bitcoin prices}
	\end{subfigure}\hfill
	\begin{subfigure}{.3\textwidth}
	\centering
	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_df_bpi.png}
	\caption{First difference of bitcoin prices}
	\end{subfigure}\hfill
	\begin{subfigure}{.3\textwidth}
	\centering
	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_log_df_bpi.png}
	\caption{Log first difference of bitcoin prices}
	\end{subfigure}
\caption{Bitcoin price development}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.85]{stata_export_graphs/ADF_twitter_variables.png}
\caption{Twitter variables stationarity test}
\label{fig:3}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.85]{stata_export_graphs/ADF_bpi_variables.png}
\caption{Bitcoin variables stationarity test}
\label{fig:4}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.85]{stata_export_graphs/LAG_crit_df_nr_tweets_df_bpi.png}
\caption{Lag Specification}
\label{fig:5}
\end{figure}

@@

\begin{table}
\centering
	\begin{tabular}{lcc} \hline
	 & (T\textsubscript{t}) & (B\textsubscript{t}) \\
	VARIABLES & df\_nr\_of\_tweets & df\_bpi\_closing\_price \\ \hline
	 &  &  \\
	L.df\_nr\_of\_tweets (T\textsubscript{t-1}) & 0.00999 (a\textsubscript{11}) & 0.00463 (a\textsubscript{21}) \\
	 & (0.0693) & (0.0104) \\
	L.df\_bpi\_closing\_price (B\textsubscript{t-1}) & -0.675 (a\textsubscript{12}) & -0.125* (a\textsubscript{22}) \\
	 & (0.469) & (0.0707) \\
	Constant  & -88.34 (c\textsubscript{1}) & -18.48 (c\textsubscript{2}) \\
	 & (177.9) & (26.79) \\
	 &  &  \\
	 Observations & 205 & 205 \\ \hline
	\multicolumn{3}{c}{ Standard errors in parentheses} \\
	\multicolumn{3}{c}{ *** p$<$0.01, ** p$<$0.05, * p$<$0.1} \\
	\end{tabular}
\caption{Var Regression}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.85]{stata_export_graphs/granger_test.png}
\caption{Granger causality test}
\label{fig:6}
\end{figure}
